{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabularx}{\textwidth}{|C|C|C|}
\hline

\textbf{should be excluded (label 1)} & 
\textbf{shouldn't be excluded (label 0)} & 
\textbf{should be excluded (label 1)}\\
\hline
First, the news is related to Taiwan's economics as it mentions Taiwan is one of the countries which have experienced an early economic rebound. Second, the news is related to Taiwan's policy as it states the expectation timing of a interest rate hike. Finally, there isn't any further discussion abount uncertainty. This news doesn't simultaneously mention economics, policy and uncertainty. Hence, it should be excluded when constructing Taiwan's EPU index.
&
First, the news is related to Taiwan's economics as the program discussed is related to economics and it's the Taiwan's Prime Minister who propose it. Second, the news is related to Taiwan's policy. Finally, the news is related to uncertainty as the writer of this news is doubt about the effectness of the policy. This news simultaneously mention economics, policy and uncertainty. Hence, it shouldn't be excluded when constructing Taiwan's EPU index.
&
First, the news is not directly related to Taiwan's economics as it discuss mainly about the global economics condition. Second, the news is not related to the policy. Finally, the news is related to the uncertainty as it discuss various downturns of the stock market in many countries. This news doesn't simultaneously mention economics, policy and uncertainty. Hence, it should be excluded when constructing Taiwan's EPU index.
\\
\hline

\textbf{shouldn't be excluded (label 0)} & 
\textbf{should be excluded (label 1)} &
\textbf{shouldn't be excluded (label 0)}\\
\hline
First, the news is related to Taiwan's economics as it points out the relation between the quality of voluntary military and the Taiwan's economics condtion. Second, the news is related to the policy regarding the voluntary military service. Finally, the news is related to the uncertainty as it discuss some possibilities and possible progress of the policy. This news simultaneously mention economics, policy and uncertainty. Hence, it shouldn't be excluded when constructing Taiwan's EPU index.
&
First, the news is related to Taiwan's economics as it's about the CEO of Mazda Taiwan expressing optimism about the domestic car market. Second, it's obvious the news isn't related to the policy. Finally, the news is related to the uncertainty as it states the existence of the uncertainty within the car market depending on the  global economics condition and the results of the election. This news doesn't simultaneously mention economics, policy and uncertainty. Hence, it should be excluded when constructing Taiwan's EPU index.
&
First, the news is related to Taiwan's economics as the main discussion is about how Korean's political situaion will affect Taiwan'e financial market. Second, the news is related to the policy as the news metion the centrial bank will try to stabalize the market. Finally, it's obvious that the news is related to the uncertainty result from the Korean's political situation. This news simultaneously mention economics, policy and uncertainty. Hence, it shouldn't be excluded when constructing Taiwan's EPU index.
\\
\hline
\end{tabularx}
}